---
title: "My Analysis"
author: "Alexa Hatcher, Hridi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
member <- read.csv("https://collinn.github.io/data/member.csv")
claims <- read.csv("https://collinn.github.io/data/claims.csv")
```

Plans of attack (:<

## Task 1

restrict to women who has greater than 18 and younger than 41

group by ID in member to see when women were insured

identify month she was delivered in and ensure she was insured in that time frame

## Task 2

Pivot wider to separate all the codes out
mutate the ICD to say what each code stands for
pivot maybe?

GGplots that investigate relationship between the outcome (opioid prescription) and explanatory values (delivery date and type, mental health disorder and migraine headache)

## Task 3

statistical model where the outcome is an opioid prescription 
- clustering data

## Task 4

report findings - summarize

Inclusion Criteria (20 pts)
– Age criteria
– Coverage criteria

Variable creation (40 points)
– Age at delivery
– delivery type
– opioid prescription status
– Migraine status
– Insurance type
– Mental Health diagnosis




